Kinematics of the Palomar 5 stellar stream from RR Lyrae stars

### 2019-10-01 paper/main.tex
new table

To represent the Pal 5 stream, we use a single Gaussian component with a fixed dispersion of $0.05~\masyr$ for the proper motion components and $0.2~\kpc$ in distance.
We have tried including the dispersions as additional parameters in our model but find that they are unconstrained; We therefore fix these values as mentioned to be smaller than the typical uncertainties.
We allow the mean of the Gaussian component to vary independently in each component as a function of $\phi_1$.
Based on the Pal 5 stream models from \citet{Bonaca:2019}, over the range of $\phi_1 \in (-20^\circ, 15^\circ)$, the mean stream trends in $\mu_1, \mu_2$, and distance $d$ can be well-approximated (within our observational uncertainties) by a quadratic function in $\phi_1$.
The mean of our stream component, $\bs{x}$, is therefore given by
\begin{equation}
    \bs{x} = \begin{pmatrix}
        \mu_1^* + b_1 \, (\phi_1 - x_1) + c_1 \, (\phi_1 - x_1)^2\\
        \mu_2^* + b_2 \, (\phi_1 - x_2) + c_2 \, (\phi_1 - x_2)^2\\
        d^* + b_d \, (\phi_1 - x_d) + c_d \, (\phi_1 - x_d)^2
        \label{eq:meanpoly}
    \end{pmatrix}
\end{equation}
where $\bs{\theta} = (\mu_1^*, \mu_2^*, d^*, b_1, b_2, b_d, c_1, c_2, c_d, x_1, x_2, x_d)$ are free parameters.

@@

\figurename~\ref{fig:trackmembers} shows a summary of the inferred membership model properties in sky position (shown in Pal 5 coordinates $\phi_1, \phi_2$), distance, $d$, and proper motion components.
\tablename~\ref{t:rrl_members} shows an abbreviated version of our catalog of RRL in the region around Pal 5, with PS1 and \Gaia~ data and membership probabilities appended.

@@

>>>>

To represent the Pal 5 stream, we use a single Gaussian component with a fixed dispersion of $0.05~\masyr$ for the proper motion components and $0.2~\kpc$ in distance.
We have tried including the dispersions as additional parameters in our model but find that they are unconstrained; We therefore fix these values as mentioned to be smaller than the typical uncertainties.
We allow the mean of the Gaussian component to vary independently in each component as a function of $\phi_1$.
Based on the Pal 5 stream models from \citet{Bonaca:2019}, over the range of $\phi_1 \in (-20^\circ, 15^\circ)$, the mean stream trends in $\mu_1, \mu_2$, and distance $d$ can be well-approximated (within our observational uncertainties) by a quadratic function in $\phi_1$.
The mean of our stream component, $\bs{x}$, is therefore given by
\begin{equation}
    \bs{x} = \begin{pmatrix}
        a_{\mu_1} + b_{\mu_1} \, (\phi_1 - x_{\mu_1}) + c_{\mu_1} \, (\phi_1 - x_{\mu_1})^2\\
        a_{\mu_2} + b_{\mu_2} \, (\phi_1 - x_{\mu_2}) + c_{\mu_2} \, (\phi_1 - x_{\mu_2})^2\\
        a_{d} + b_d \, (\phi_1 - x_d) + c_d \, (\phi_1 - x_d)^2
        \label{eq:meanpoly}
    \end{pmatrix}
\end{equation}
where $\bs{\theta} = (a_{\mu_1}, a_{\mu_2}, a_d, b_{\mu_1}, b_{\mu_2}, b_d, c_{\mu_1}, c_{\mu_2}, c_d, x_{\mu_1}, x_{\mu_2}, x_d)$ are free parameters.

@@

\figurename~\ref{fig:trackmembers} shows a summary of the inferred membership model properties in sky position (shown in Pal 5 coordinates $\phi_1, \phi_2$), distance, $d$, and proper motion components.
\tablename~\ref{t:rrl_members} shows an abbreviated version of our catalog of RRL in the region around Pal 5, with PS1 and \Gaia~ data and membership probabilities appended.
\changes{\tablename~\ref{t:trendpars} contains the maximum a posteriori trend parameter values from the above analysis.}

@@

\begin{table}
\begin{center}
\caption{Maximum a posteriori proper motion and distance trend parameters (see \sectionname~\ref{sec:membership}). The constant terms have units $\masyr$ and $\kpc$ for proper motion and distance parameters, respectively. The angular units are in degrees such that, e.g., the linear coeff $b_d$ has units of $\kpc~\textrm{deg}^{-1}$.}\label{t:trendpars}
\begin{footnotesize}
\begin{tabular}{c c c c c}
\toprule
y & $x_{\textrm{y}}$ & $a_\textrm{y}$ & $b_\textrm{y}$ & $c_\textrm{y}$\\
param. name & reference $\phi_1$ & constant & linear coeff. & quadratic coeff.\\
\midrule
$\mu_1$ &  $-1.072$ & 3.740  & $4.102 \times 10^{-2}$  & $-6.423 \times 10^{-4}$ \\
$\mu_2$ & $-10.954$ & 0.686  & $-2.826 \times 10^{-2}$ & $2.832 \times 10^{-3}$ \\
$d$     & $-16.081$ & 22.022 & $9.460 \times 10^{-3}$  & $-6.327 \times 10^{-3}$\\
\bottomrule
\end{tabular}
\end{footnotesize}
\end{center}
\end{table}
